---
title: "Interactive Visualization"
author: "Christoffer Tan"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("data_processing.R")
```

## What the Data Reveals {.tabset}
The following interactive visualizations highlight key insights from the final project analysis, demonstrating how weather conditions and time-of-day influence bike share usage in Toronto. Each figure provides a unique perspective: from the hourly distribution of ridership to evaluating the accuracy and feature importance of predictive models. These interactive tools allow you to explore patterns and relationships within the data, offering intuitive insights into factors that shape urban bike-sharing behaviors.

### 📊 Hourly Distribution of Total Bike Trips
<div style="text-align: center;">
```{r, echo=FALSE, warning=FALSE, style="display: flex; justify-content: center;"}
p1
```
</div> <p style="font-size: 100%; margin-top: -15px; text-align: center;"> <strong>Figure 1.</strong> An interactive boxplot showing hourly bike trip distribution. Usage peaks around 8 AM and 5 PM, with lower volumes overnight. </p> 

Bike usage demonstrates significant variability across the day, peaking notably during commuting hours (8 AM and 5 PM). Early morning (12 AM - 6 AM) and late-night (after 9 PM) hours exhibit lower and more stable ridership, indicating predictable usage patterns. You can hover over each box to see specific statistical details for each hour.


### 🌡️ Feature Importance (Random Forest)
<div style="text-align: center;">
```{r, echo=FALSE, warning=FALSE, style="display: flex; justify-content: center;"}
p2
```
</div> <p style="font-size: 100%; margin-top: -15px; text-align: center;"> <strong>Figure 2.</strong> An interactive horizontal bar plot visualizing the relative importance (%IncMSE) of predictors in the Random Forest model, which achieved the best performance among tested models.</p> 

This visualization highlights the most influential features contributing to the predictive accuracy of the best-performing Random Forest model. The "hour of day" is clearly the strongest predictor, followed by "temperature" and "humidity." Weather conditions such as wind speed and cloudiness have comparatively smaller yet notable impacts. Hover over each bar to see exact importance values.


### 📈 Predicted vs. Actual Bike Trips
<div style="text-align: center;">
```{r, echo=FALSE, warning=FALSE, style="display: flex; justify-content: center;"}
p3
```
</div> <p style="font-size: 100%; margin-top: -15px; text-align: center;"> <strong>Figure 3.</strong> An interactive scatter plot comparing predicted bike trip counts against actual observations from the test dataset, using predictions generated by the best-performing Random Forest model. Points are colored by the absolute prediction error.</p> 

This plot visually evaluates the accuracy of predictions from the best Random Forest model. Points near the dashed diagonal indicate accurate predictions, while deviations represent prediction errors. The color gradient illustrates that the model predicts accurately for most observations, though some underprediction is apparent during peak demand hours. Hover over points to inspect individual prediction details and errors.
